Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-17 cordillera-cycle.tex
Add MIS 2 and MIS 4 ice configuration maps.

@@

>>>>

% avoid "too many unprocessed floats" errors
\clearpage

@@

% fig:mis2
\begin{figure*}
  \includegraphics{icemaps-mis2}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~2 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis2}
\end{figure*}

% fig:mis4
\begin{figure*}
  \includegraphics{icemaps-mis4}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~4 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis4}
\end{figure*}
